### 2021-05-09 papers/SYRCoSE/regmachine-eventstruct.tex
grammar

The construction starts from an initial event structure
containing, for each thread, an event labelled by $\tslab{}$.
We depict the corresponding thread state below the label.
Initially, each event is mapped to an initial thread state
consisting of an instruction pointer pointing to the first 
instruction to be executed and an initial mapping of registers
denoted as $\bot$.
The first step executes the store instruction from 
the leftmost thread and exits the program, 
since the execution of this thread terminates
(we omit the $\exitInst$ instructions at the end of each thread for brevity).
Next, the store from the rightmost thread is executed and corresponding
write event gets added to the structure. 
After that the load instruction from the middle thread is executed. 
Since there are two matching write events in the event structure, 
two conflicting reads are conjoined to the event structure. 
Note that the events can be added non-deterministically in any order
respecting causality. We could have first executed the rightmost thread
and added write $\wlab{x}{2}$ before $\wlab{x}{1}$, 
or we could have added the read with label $\rlab{x}{2}$ 
before another read $\rlab{x}{1}$.

@@

The rules of operational semantics constructing 
the event structure are presented on~\cref{fig:eventstruct-sem}.
The first auxiliary rule \ESAddEventRule~ adds a new event, sets its 
label, $\lPO$ and $\lRF$ predecessors. 
The \ESIdleRule~ handles the case when a thread of 
the register machine performs an internal step 
without any side effect. 
It chooses an event~$e$ together with 
the thread state~$s$ corresponding to it
and performs one step reduction to a new state~$s'$.
It then updates the mapping of events to thread states.   
The last three rules \ESStoreRule, \ESLoadRule, and \ESLoadBotRule~
correspond to store and load performed by some thread.  
Similarly to \ESIdleRule, an event $e_{\lPO}$ is selected
and one reduction is performed from the corresponding thread state~$s$.
Unlike the \ESIdleRule~ case, however, a new event~$e$ is also generated.
In case of \ESLoadRule~ additionally an event~$e_{\lRF}$ is selected,
such that it has a write label matching the read label of the new event.    
The rule \ESLoadBotRule~ corresponds to a case when load 
is performed ``too early'', before any write to the given location is available.

>>>>

The construction starts from an initial event structure
containing, for each thread, an event labelled by $\tslab{}$.
We depict the corresponding thread state below each label.
Initially, each event is mapped to an initial thread state
consisting of an instruction pointer pointing to the first 
instruction to be executed and an initial mapping of registers
denoted as $\bot$.
The first step executes the store instruction from 
the leftmost thread and exits the program, 
since the execution of this thread terminates
(we omit the $\exitInst$ instructions at the end of each thread for brevity).
Next, the store from the rightmost thread is executed and the corresponding
write event gets added to the structure. 
After that, the load instruction from the middle thread is executed. 
Since there are two matching write events in the event structure, 
two conflicting reads are conjoined to the event structure. 
Note that the events can be added non-deterministically in any order
respecting causality. We could have first executed the rightmost thread
and added write $\wlab{x}{2}$ before $\wlab{x}{1}$, 
or we could have added the read with label $\rlab{x}{2}$ 
before another read $\rlab{x}{1}$.

@@

The rules of operational semantics constructing 
the event structure are presented in~\cref{fig:eventstruct-sem}.
The first auxiliary rule \ESAddEventRule~ adds a new event, sets its 
label, $\lPO$ and $\lRF$ predecessors. 
The \ESIdleRule~ handles the case when a thread of 
the register machine performs an internal step 
without any side effect. 
It chooses an event~$e$ together with 
the thread state~$s$ corresponding to it
and performs one step reduction to a new state~$s'$.
It then updates the mapping of events to thread states.   
The last three rules \ESStoreRule, \ESLoadRule, and \ESLoadBotRule~
correspond to store and load performed by some thread.  
Similarly to \ESIdleRule, an event $e_{\lPO}$ is selected
and one reduction is performed from the corresponding thread state~$s$.
Unlike the \ESIdleRule~ case, however, a new event~$e$ is also generated.
In case of \ESLoadRule~ additionally an event~$e_{\lRF}$ is selected,
such that it has a write label matching the read label of the new event.    
The rule \ESLoadBotRule~ corresponds to a case when load 
is performed ``too early'', before any write to the given location is available.
